Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-01-03 paper/ms.tex
Finish caption in one orbit fig

\begin{figure*}
\plotone{fig/one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here an orbit with
initial position $(8,0,0)\,\kpc$ and initial velocity $(0,-190,50)\,\kms$.
This corresponds to an orbit with actions $(J_r, L_z, J_z) = (32.5, -1520,
23.0)\,\actunit$ and $z_{\text{max}}=854\,\pc$. Considering the first $\Gyr$
of this orbit, we assume an immortal observer }
\label{fig:one_orbit_wrong_ref}
\end{figure*}

>>>>

\begin{figure*}
\plotone{fig/one_orbit.pdf}
\caption{The artificial phase-dependence in the observed actions induced by an
error in the Galactocentric coordinate system. We consider here an orbit with
initial position $(8,0,0)\,\kpc$ and initial velocity $(0,-190,30)\,\kms$.
This corresponds to an orbit with actions $(J_r, L_z, J_z) = (37.9, -1520,
7.0)\,\actunit$ and $z_{\text{max}}=425\,\pc$. We integrate the orbit
according to the procedure laid out in Section~\ref{ssec:action_comp}. Then,
we subtract $100\,\pc$ from the $z$ value of each position in the orbit,
corresponding to an erroneous observer assuming a midplane that is off by
$100\,\pc$. We then allow our (immortal) observer to observe the orbit over
$1\,\Gyr$ and perform the same orbit integration procedure at each timestep,
and report the values of the actions. The computation of $L_z$ is pristine to
errors in $z$, with only numerical artifacts remaining. Only small errors are
induced in $J_r$, with the middle $90\%$ of values over the $\Gyr$ being
$\sim6\%$ of the true $J_r$. As expected, large errors are induced in $J_z$,
with the middle $90\%$ of values being $\sim85\%$ of the true $J_z$.}
\label{fig:one_orbit_wrong_ref}
\end{figure*}
